### 2020-01-29 wuhan.tex
keep making changes

Here, we use the gamma approximation framework \citep{park2019practical} to first characterize the
amount of uncertainty present in the underlying parameters and then assess the 
degree to which these uncertainties
affect the estimate of $\mathcal R_0$.
Assuming that generation intervals follow a gamma distribution 
with the mean $\bar G$ and the squared coefficient of variation $\kappa$, 
we have
\begin{equation}
\mathcal R_0 = \left(1 + \kappa r \bar{G}\right)^{1/\kappa}.
\label{eq:gamma}
\end{equation}
This equation demonstrates that a generation-interval distribution
that has a larger mean (higher $\bar{G}$) or is less variable (lower $\kappa$)
will give a higher estimate of $\mathcal R_0$ for the same value of $r$.

First, we gathered information on estimates of $\mathcal R_0$ and their
assumptions about the underlying generation-interval distributions from
6 articles that were uploaded to
preprint servers (e.g., bioRxiv, medRxiv, and SSRN) between January 24th, 2020 and January 26th, 2020.
For each study $i$, we model $\mathcal R_0$, $\bar G$, and $\kappa$ with an appropriate probability distribution (either uniform or gamma) that roughly matches the estimated or assumed values and their uncertainty ranges:
\begin{equation}
\begin{aligned}
\mathcal R_{0i} &\sim D_{i, \mathcal R}(\theta_{i, \mathcal R})\\
{\bar G}_i &\sim D_{i, G}(\theta_{i, G})\\
\kappa_i &\sim D_{i, \kappa}(\theta_{i, \kappa})\\
\end{aligned}
\end{equation}
where $D$ is a probability distribution and $\theta$ is a parameter set of the probability distribution $D$.
For example, one study estimated $\mathcal R_0 = 2.6$ (95\% CI: 1.5--3.5);
we model this parameter as a gamma distribution with mean of 2.6 and a shape parameter of 28, which has a 95\% probability of containing a value between 1.5 and 3.5.
Then, we draw 100,000 random samples from these distributions ($\mathcal R_{0i}^n$, ${\bar G}_i^n$, and $\kappa_i^n$ where $n = 1, \dots, 100,000$) and calculate the exponential growth rate $r$ via the inverse of \eref{gamma}:
\begin{equation}
r_i^n = \frac{{\mathcal R_{0i}^n}^{\kappa_i^n} - 1}{\kappa_i^n \bar{G}_i^n}.
\end{equation}
This allows us to approximate the probability distribution of the exponential growth rate as a discrete probability distribution.

>>>>

Here, we use the gamma approximation framework \citep{park2019practical} to first characterize the
amount of uncertainty present in the underlying parameters and then assess the 
degree to which these uncertainties
affect the estimate of $\mathcal R_0$.
Assuming that generation intervals follow a gamma distribution 
with the mean $\bar G$ and the squared coefficient of variation (CV$^2$) $\kappa$, 
we have
\begin{equation}
\mathcal R_0 = \left(1 + \kappa r \bar{G}\right)^{1/\kappa}.
\label{eq:gamma}
\end{equation}
This equation demonstrates that a generation-interval distribution
that has a larger mean (higher $\bar{G}$) or is less variable (lower $\kappa$)
will give a higher estimate of $\mathcal R_0$ for the same value of $r$.

\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & 2.5 (1.5--3.5)$^\ast$ & 8.4 & unspecified$^\dagger$ \\
\hline
Study 2 & 2.92 (95\% CI: 2.28--3.67) & 8.4 & 0.2 \\
\hline
Study 3 & 2.0--3.1 & 6--10 & 0 \\
\hline
Study 4 & 3.8 (95\% CI: 3.6--4.0) & 7.6 & 0.5 \\
\hline
Study 5 & 2.2 (90\% CI: 1.4--3.8) & 7--14 & 0.5\\
\hline
Study 6 & 5.47 (95\% CI: 4.16--7.10)$^\ddagger$ & 7.6--8.4 & 0.2
\end{tabular}
\end{center}
\caption{
\textbf{Estimates of the basic reproductive number and their assumptions about the generation-interval distributions.}
$^\ast$We treated these intervals as a 95\% confidence interval in our analysis.
$^\dagger$We assumed $\kappa = 0.5$ in our analysis.
$^\ddagger$The authors presented $\mathcal R_0$ estimates under different assumptions; we used their baseline scenario in our analysis.
}
\end{table}

First, we gathered information on estimates of $\mathcal R_0$ and their
assumptions about the underlying generation-interval distributions from
6 articles that were uploaded to
preprint servers between January 24th, 2020 and January 26th, 2020 (Table 1).
For each study $i$, we model $\mathcal R_0$, $\bar G$, and $\kappa$ with an appropriate probability distribution (either uniform or gamma) that roughly matches the estimated or assumed values and their uncertainty ranges:
\begin{equation}
\begin{aligned}
\mathcal R_{0i} &\sim D_{i, \mathcal R}(\theta_{i, \mathcal R})\\
{\bar G}_i &\sim D_{i, G}(\theta_{i, G})\\
\kappa_i &\sim D_{i, \kappa}(\theta_{i, \kappa})\\
\end{aligned}
\end{equation}
where $D$ is a probability distribution and $\theta$ is a parameter set of the probability distribution $D$.
For example, Study 2 estimated $\mathcal R_0 = 2.92$ (95\% CI: 2.28--3.67);
we model this parameter as a gamma distribution with mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for the list of all distributions).
Then, we draw 100,000 random samples from these distributions ($\mathcal R_{0i}^n$, ${\bar G}_i^n$, and $\kappa_i^n$ where $n = 1, \dots, 100,000$) and calculate the exponential growth rate $r$ via the inverse of \eref{gamma}:
\begin{equation}
r_i^n = \frac{{\mathcal R_{0i}^n}^{\kappa_i^n} - 1}{\kappa_i^n \bar{G}_i^n}.
\end{equation}
This allows us to approximate the probability distribution of the exponential growth rate as a discrete probability distribution.

\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & $\mathrm{Gamma}(\alpha=28, \beta=28/2.6)$ & constant & constant \\
\hline
Study 2 & $\mathrm{Gamma}(\alpha=67, \beta=67/2.92)$ & constant & constant \\
\hline
Study 3 & N.A. & $\mathrm{Uniform}(6, 10)$ & constant\\
\hline
Study 4 & $\mathrm{Gamma}(\alpha=1400, \beta=1400/3.8)$ & constant & constant \\
\hline
Study 5 & $\mathrm{Gamma}(\alpha=12, \beta=12/2.2)$ & $\mathrm{Uniform}(7, 14)$ & constant\\
\hline
Study 6 & $\mathrm{Gamma}(\alpha=54, \beta=54/5.47)$ & $\mathrm{Uniform}(7.6, 8.4)$ & constant
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions for the estimates of $\mathcal R_0$ and for the assumed values of $\bar G$ and $\kappa$.}
The probability distribution for the exponential growth rate $r$ for each study is obtained by drawing random samples from these distributions and taking the inverse of \eref{gamma}.
The gamma distribution is parameterized by shape $\alpha$ and rate $\beta$ parameters.
Constant distributions assume a fixed values according to Table 1.
}
\end{table}
